
\documentclass[]{deedy-resume-openfont}


\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Amol Suraj}{Mishra}{ 
\href{mailto:amolsuraj.vit5@gmail.com}{amolsuraj.vit5@gmail.com}~\textbullet~ {9994025766\\}
{744, Men’s Hostel - L Block, VIT Vellore, Vellore, India\\}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{M.Tech in Software Engg}
\descript{VIT University, Vellore}
\location{Cum. GPA: 9.72 \\ Rank: 2/475}
\sectionsep

\subsection{High School}
\descript{DAV Public School, Hyderabad}
\location{Percentage : 90}
\sectionsep

\subsection{Secondary School}
\descript{Karuna School, Sangareddy}
\location{Percentage : 95}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/amolmishra23}{\custombold{amolmishra23}} \\
LinkedIn://  \href{https://www.linkedin.com/in/amol-suraj-mishra-598851125}{\custombold{amol-suraj-mishra-598851125}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming languages}
R \textbullet{}   Python \textbullet{} Java \textbullet{} SQL \\
C\# \textbullet{} C++ \textbullet{} C\\ 
\subsection{Tools/Frameworks}
MATLAB \textbullet{} Oracle \textbullet{} Microsoft Office \textbullet{} GIT \textbullet{} Latex \textbullet{} Django \\
\subsection{Operating Systems}
Windows \textbullet{} Ubuntu \\
\subsection{Non Technical Skills}
People \textbullet{} Networking \textbullet{} Presentation \textbullet{} Documentation \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES KNOWN
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages known}
English - Full professional proficiency\\
Hindi - Full professional proficiency\\
Telugu - Full professional proficiency\\
French - Elementary proficiency\\
Maithili - Native or bilingual proficiency\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HOBBIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobbies}
Finding online deals\\
Downloading stuff\\
Fixing issues\\
Reading quora\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
Coding\\
Solving puzzles\\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CAREER OBJECTIVE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Career Objective}
Results-driven and diligent professional seeking a Software Engineer position with Core Concepts utilizing strong technical acumen, logical thinking and relevant expertise to provide the company with the best software solutions.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\RaggedRight
\runsubsection{VIT UNIVERSITY}
\descript{| Program Representative }
\location{July 2016 – Present | Vellore, Tamil nadu}
{\justifying \noindent Representing the needs and expectations of my peer group to the management, regarding the curriculum operational requirements of the university by filling the gap between them and the management. \par}

\sectionsep

\runsubsection{IIT BOMBAY}
\descript{| Summer Research Intern }
\location{May 2017 – July 2017 | Mumbai, Maharastra}
{\justifying \noindent Research work for the enhancement of IITBombayX platform. Project was to create an Open-edX server task automator using XBlock, which will perform all the tasks which a system administrator frequently performs in the lifecycle of the Open edX server.\par}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Comprehensive data mining, visualization and predictive analysis on IPL using machine learning \\}
{\justifying \noindent Web application that performs detailed analysis and visualization of various features, ranking of players, prediction of match results built using IPL season 1 to 10 dataset in R language. \par}
\sectionsep

\runsubsection{Swiftkey text prediction model \\}
{\justifying \noindent Web application that makes next-word prediction using the concept of n-grams in NLP, built using textual data from twitter, news and blogs. \par}
\sectionsep

\runsubsection{Sentiment Analysis using NLTK, TextBlob — Comparison\\}
{\justifying \noindent Web application for getting the sentiment polarity of real-time tweets from Twitter and plotting them.
\sectionsep \par}

\runsubsection{Travel assistance system for visually impaired person \\}
{\justifying \noindent This application makes the travel of a visually impaired person easy, when he travels on bus. Made using SERVLETS in JAVA. \par}
\sectionsep

\runsubsection{Simple Text Editor in JAVA using AWT \\}
{\justifying \noindent Simple notepad like text editor with productive functionalities and shortcuts for preparing a text document made using JAVA AWT. \par}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certificates} 

\begin{tabular}{rll}
John’s Hopkins University(Coursera) & Data Science Specialization\\
Stanford University(Coursera) & Machine Learning\\
University Of Michigan(Coursera) & Getting Started with Python\\
University Of Michigan(Coursera) & Python Data Structures\\
GDG VIT Vellore Google Developers & Android Study Jams
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2016,2017,2018	     & Chancellor's Merit Scholarship Award\\
2018	     & VIT Achiever's Award\\
\end{tabular}

\sectionsep



\end{minipage} 
\end{document}